Optimizing the Cobb Doughlas Habitability Production function using Particle Swarm Optimization

### 2017-11-27 docs/report/draft.tex
Added content to report.

In this paper, \pso\ has been applied to estimate the Cobb Douglas Habitability Score of an exoplanet. The score is
estimated by maximizing the Cobb-Douglas Habitability Production Function. The function considers four parameters,
radius, mass, escape velocity and surface temperature, taken from the Exoplanets Catalog hosted by the Planetary
Habitability Laboratory, UPR Arecibo. Since the Cobb-Douglas function is concave under certain constraints, the
problem can be reduced to a convex optimization over the negative of the production function.

\section{Cobb-Douglas Habitability Score}

\subsection{Cobb-Douglas Habitability Production Function}
The general form of the Cobb-Douglas production function is given by,
\begin{equation}
  Y = k\cdot{(x_1)}^\alpha\cdot{(x_2)}^\beta,
\end{equation}
where $k$ is a constant that may be set according to requirement, $x_1$ and $x_2$ are the input parameters to the
function, $Y$ is the total output production value, and $\alpha$ and $\beta$ are called the elasticity coefficients.

% \begin{pointers}
% \item Describe the Cobb Douglas Habitability Score.
% \item Describe CRS, DRS and IRS\@.
% \item Splitting the CDHS score into two values.
% \item State the equations.
% \item Score is estimated by maximizing the CDHPF fn.
% \end{pointers}

>>>>

In this paper, \pso\ has been applied to estimate the Cobb Douglas Habitability Score (CDHS) of an exoplanet. The score
is estimated by maximizing the Cobb-Douglas Habitability Production Function (CD-HPF). The function considers four
parameters, radius, mass, escape velocity and surface temperature, taken from the Exoplanets Catalog hosted by the
Planetary Habitability Laboratory, UPR Arecibo. Since the Cobb-Douglas function is concave under certain constraints,
the problem can be reduced to a convex optimization over the negative of the production function.

\section{Cobb-Douglas Habitability Score}
% Add the citations to Saha's papers.

\subsection{Cobb-Douglas Production Function}
The general form of the Cobb-Douglas production function (CD-PF) is given by,
\begin{equation}
  Y = k\cdot{(x_1)}^\alpha\cdot{(x_2)}^\beta,
\end{equation}
where $k$ is a constant that may be set according to requirement, $x_1$ and $x_2$ are the input parameters to the
function, $Y$ is the total output production value, and $\alpha$ and $\beta$ are called the elasticity coefficients.

The CDHS is estimated by maximizing the CD-PF when the returns to scale are either decreasing or constant. This is
marked by two constraints on the elasticity coefficients,
\begin{itemize}
\setlength\itemsep{0pt}
\item When $\alpha+\beta < 1$, the CD-PF observes decreasing returns to scale.
\item When $\alpha+\beta = 1$, the CD-PF observes constant returns to scale.
\end{itemize}
Further, if $0 < \alpha, \beta < 1$, the CD-PF is concave, and therefore has a maxima. The CD-PF can be adapted as a
Habitability Production Function by setting the input parameters to the measurable parameters of an exoplanet and using
these to estimate the elasticity coefficients.

\subsection{Cobb-Douglas Habitability Score Estimation}
Two types of Habitability Scores are calculated for each planet, the interior CDHS (CDHS\textsubscript{i}) and the
surface CDHS (CDHS\textsubscript{s}), given by the following equations,
\begin{subequations}
  \begin{alignat}{4}
    Y_1 &=\ {CDHS}_i\ &=\ &D^\alpha\ & \cdot\ &R^\beta\ &,\\
    Y_2 &=\ {CDHS}_s\ &=\ &{V_e}^\gamma\ & \cdot\ &{T_s}^\delta\ &,
  \end{alignat}
\end{subequations}
where, $D$, $R$, $V_e$ and $T_s$ are density, radius, escape velocity and surface temperature respectively. The final
CDHS score is convex combination of the interior and surface CDHS values as given by,
\begin{equation}
  Y = w'\cdot Y_1 + w''\cdot Y_2,
\end{equation}

% Algorithm for CDHS estimation and explanation.
